The five axes of the Turtle: symmetry and asymmetry in NGC~6210

### 2020-10-03 ms.tex
Collate usepackages in a file
This was to make things work better on iPad, but it didn't help much.
I also protected some command with if-blocks in order to support older
TeX distros.
Update latex file to use new version of figure 2
Update LaTeX file for all Lower-case slit letter figures

\documentclass[useAMS, usenatbib]{mnras}
\pdfsuppresswarningpagegroup=1
%
\usepackage[spanish,es-minimal,english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}

\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{siunitx}
\usepackage{newtxtext}
\usepackage[stix2,smallerops]{newtxmath}
\usepackage{booktabs}
\hypersetup{colorlinks=True, linkcolor=blue!50!black, citecolor=black,
  urlcolor=blue!50!black}
\usepackage{etoolbox}
\robustify\bfseries
\robustify\itshape

@@

\section{Longslit Spectroscopy}
\label{sec:observations}
 \begin{figure}
   \centering
   \includegraphics[width=0.38\textwidth]{tere-figs/Figure2a}
   \caption{
     Spectrograph slit positions for vertical orientations (upper panel),
     horizontal orientations (middle panel),
     and diagonal orientations (lower panel).
     Background image in each case is an \textit{HST} \oiii{} image of the nebula.
     In the top panel, slit positions from the 2015 season are indicated as solid lines
     and positions from other seasons are shown as dashed lines (see Table~\ref{table:pa5} for details). 
   }
  \label{fig:slit-positions}
\end{figure}

\begin{table}
\centering
\caption{OAN MES-SPM high-resolution spectroscopy of NGC~6210}
\label{table:pa5}
\begin{tabular}{@{}l@{} rrrr l@{}} \toprule
  Epoch&   Exposure & Spectral  & Width & P.A.   & Slit Label\\
     &    (s) & Range  &  (\si{\um})    &    (\(^\circ\))  &  \\
  \midrule
  {(1)} & {(2)} & {(3)} & {(4)} & {(5)} & {(6)} \\
    \addlinespace
1998/06/28 & 30 & \Ha  & 150 & 90 & O\\
1998/06/28 & 300 & \Ha  & 150 & 90 & N\\
1998/06/28 & 1200 & \Ha   & 150 & 90 & M,P,Q \\
2003/06/05 & 1800 &  \Ha   & 70 &0 &     A,B,D*,E*,F,H,I,K\\ 
2003/10/16 &  1800 &   \Ha    & 70 & $-$21 & T\\
2003/10/16 &  1800 &   \Ha   & 70 & $-$68 & V\\
2003/10/17 &  1800 &   \Ha  & 70 & 77 & W\\
2004/06/13 & 1800 &   \oiii  & 70 & $-$9 & R  \\  
2004/06/14 & 1800 &  \sii &150 & $-$19 & S  \\
2004/06/13 & 1800 &   \oiii  & 70 & $-$19 & S  \\  
2004/06/13 & 1800 &   \oiii  & 70 & $-$56 & U  \\  
2004/06/14 & 1800 &   \oiii  & 150 & 0 & A',L  \\
2011/05/21 & 1800 & \Ha  & 150 & 0 & G* \\
2011/05/21 & 600 & \oiii & 150 & 0  & G \\
2013/07/06 &  1800 & \Ha   & 150 & 0 & C,I,J \\
2015/08/18 &  1800 &   \Ha, \oiii  & 70 & 0 & C,D,E,F,G\\
2015/08/19 &  1800 &   \Ha, \oiii   & 70 & 0 & B,A*,I\\
2015/08/20 &  1800 &   \Ha, \oiii & 70 & 0 & H,J,K\\
2019/09/18 &  1800 &   \Ha    & 150 & 56 & X\\
  \bottomrule
  \addlinespace
  \multicolumn{6}{@{}p{\columnwidth}@{}}{
  \textsc{Columns:}
  (1)~Date of each observing run.
  (2)~Length of each spectroscopic exposure.
  (3)~Spectral range of each observation.  \Ha{} includes \nii{} \Wav{6548, 83} and \heii{} \Wav{6560}.  \sii{} includes both doublet lines \Wav{6716, 31}.
  (4)~Slit width in microns.
  (5)~Position angle of slit orientation in degrees.
  (6)~Labels assigned to each slit position, see Fig.~\ref{fig:slit-positions}.
  }
\end{tabular}
\end{table}

@@

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/turtle-peanut-map-lores}
  \caption{
    Velocity features in the high-ionization shells,
    which have been identified in the \oiii{} slits.
    Left panel shows blue-shifted features,
    while right panel shows red-shifted features,
    each labelled with their line-of-sight velocity
    with respect to the nominal systemic velocity of \SI{-40}{km.s^{-1}}.
    Solid lines show features in the inner shell,
    dashed lines show features in the intermediate shell,
    and dot-dashed lines show miscellaneous features between the two shells.
    The line width is a qualitative indicator of the brightness of each feature.
    The background grayscale shows a high-pass filtered version of the HST \oiii{} image.
  }
  \label{fig:shell-velocity-components}
\end{figure*}

@@

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/turtle-knot-complex-map-lores}
  \caption{
    Velocity features in the low-ionization knot complexes,
    which have been identified in the \nii{} slits.
    Left panel shows blue-shifted features,
    while right panel shows red-shifted features,
    each labelled with their line-of-sight velocity
    with respect to the nominal systemic velocity of \SI{-40}{km.s^{-1}}.
    The line width is a qualitative indicator of the brightness of each feature.
  }
  \label{fig:knot-complex-map}
% \end{figure*}

% \begin{figure*}
%   \centering
  \bigskip
  \includegraphics[width=\linewidth]
  {figs/turtle-lobes-simplified-components-lores}
  \caption{
    Velocity components in the outer lobes,
    which have been identified in the \oiii{} slits.
    (a)~Blue-shifted components identified in individual slits.
    (b)~Red-shifted components identified in individual slits.
  }
  \label{fig:outer-lobe-components}
\end{figure*}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/turtle-halo-map-lores}
  \caption{
    Velocity components in the halo, all measured from the \oiii{} spectra with slit positions as indicated.
    Components are divided into three classes:
    inner halo (pink ellipses), outer halo (yellow ellipses),
    and halo knots (green ellipses).
    The inner portion of the background image is
    the same high-pass-filtered \textit{HST} image
    shown in Figs.~\ref{fig:shell-velocity-components} and~\ref{fig:outer-lobe-components}.
    The outer portion of the background image is a deep \oiii{} exposure of the halo
    obtained with MES-SPM in direct imaging mode with an occulting bar (see Fig.~\ref{fig:halo-knots}).
  }
  \label{fig:halo-components}
\end{figure}

>>>>

\documentclass[useAMS, usenatbib]{mnras}
\usepackage{wjh-packages}
\usepackage{booktabs}
\hypersetup{colorlinks=True, linkcolor=blue!50!black, citecolor=black,
  urlcolor=blue!50!black}
\usepackage{etoolbox}
\robustify\bfseries
\robustify\itshape

@@

\section{Longslit Spectroscopy}
\label{sec:observations}
 \begin{figure}
   \centering
   \includegraphics[width=0.38\textwidth]{figs/turtle-slits}
   \caption{
     Spectrograph slit positions for vertical orientations (upper panel),
     horizontal orientations (middle panel),
     and diagonal orientations (lower panel).
     Background image in each case is an \textit{HST} \oiii{} image of the nebula.
     In the top panel, slit positions from the 2015 season are indicated as solid lines
     and positions from other seasons are shown as dashed lines (see Table~\ref{table:pa5} for details). 
   }
  \label{fig:slit-positions}
\end{figure}

\begin{table}
\centering
\caption{OAN MES-SPM high-resolution spectroscopy of NGC~6210}
\label{table:pa5}
\begin{tabular}{@{}l@{} rrrr l@{}} \toprule
  Epoch&   Exposure & Spectral  & Width & P.A.   & Slit Label\\
     &    (s) & Range  &  (\si{\um})    &    (\(^\circ\))  &  \\
  \midrule
  {(1)} & {(2)} & {(3)} & {(4)} & {(5)} & {(6)} \\
    \addlinespace
1998/06/28 & 30 & \Ha  & 150 & 90 & o\\
1998/06/28 & 300 & \Ha  & 150 & 90 & n\\
1998/06/28 & 1200 & \Ha   & 150 & 90 & m,p,q \\
2003/06/05 & 1800 &  \Ha   & 70 &0 &     a,b,d*,e*,f,h,i,k\\ 
2003/10/16 &  1800 &   \Ha    & 70 & $-$21 & t\\
2003/10/16 &  1800 &   \Ha   & 70 & $-$68 & v\\
2003/10/17 &  1800 &   \Ha  & 70 & 77 & w\\
2004/06/13 & 1800 &   \oiii  & 70 & $-$9 & r  \\  
2004/06/14 & 1800 &  \sii &150 & $-$19 & s  \\
2004/06/13 & 1800 &   \oiii  & 70 & $-$19 & s  \\  
2004/06/13 & 1800 &   \oiii  & 70 & $-$56 & u  \\  
  2004/06/14 & 1800 &   \oiii  & 150 & 0 & a\(\prime\),l  \\
2011/05/21 & 1800 & \Ha  & 150 & 0 & g* \\
2011/05/21 & 600 & \oiii & 150 & 0  & g \\
2013/07/06 &  1800 & \Ha   & 150 & 0 & c,i,j \\
2015/08/18 &  1800 &   \Ha, \oiii  & 70 & 0 & c,d,e,f,g\\
2015/08/19 &  1800 &   \Ha, \oiii   & 70 & 0 & b,a*,i\\
2015/08/20 &  1800 &   \Ha, \oiii & 70 & 0 & h,j,k\\
2019/09/18 &  1800 &   \Ha    & 150 & 56 & x\\
  \bottomrule
  \addlinespace
  \multicolumn{6}{@{}p{\columnwidth}@{}}{
  \textsc{Columns:}
  (1)~Date of each observing run.
  (2)~Length of each spectroscopic exposure.
  (3)~Spectral range of each observation.  \Ha{} includes \nii{} \Wav{6548, 83} and \heii{} \Wav{6560}.  \sii{} includes both doublet lines \Wav{6716, 31}.
  (4)~Slit width in microns.
  (5)~Position angle of slit orientation in degrees.
  (6)~Labels assigned to each slit position, see Fig.~\ref{fig:slit-positions}.
  }
\end{tabular}
\end{table}

@@

\begin{figure*}
  \centering
  % \includegraphics[width=\linewidth]{figs/turtle-peanut-map-lores}
  \includegraphics[width=\linewidth]{figs/turtle-peanut-map}
  \caption{
    Velocity features in the high-ionization shells,
    which have been identified in the \oiii{} slits.
    Left panel shows blue-shifted features,
    while right panel shows red-shifted features,
    each labelled with their line-of-sight velocity
    with respect to the nominal systemic velocity of \SI{-40}{km.s^{-1}}.
    Solid lines show features in the inner shell,
    dashed lines show features in the intermediate shell,
    and dot-dashed lines show miscellaneous features between the two shells.
    The line width is a qualitative indicator of the brightness of each feature.
    The background grayscale shows a high-pass filtered version of the HST \oiii{} image.
  }
  \label{fig:shell-velocity-components}
\end{figure*}

@@

\begin{figure*}
  \centering
  % \includegraphics[width=\linewidth]{figs/turtle-knot-complex-map-lores}
  \includegraphics[width=\linewidth]{figs/turtle-knot-complex-map}
  \caption{
    Velocity features in the low-ionization knot complexes,
    which have been identified in the \nii{} slits.
    Left panel shows blue-shifted features,
    while right panel shows red-shifted features,
    each labelled with their line-of-sight velocity
    with respect to the nominal systemic velocity of \SI{-40}{km.s^{-1}}.
    The line width is a qualitative indicator of the brightness of each feature.
  }
  \label{fig:knot-complex-map}
% \end{figure*}

% \begin{figure*}
%   \centering
  \bigskip
  \includegraphics[width=\linewidth]
  {figs/turtle-lobes-simplified-components}
  % {figs/turtle-lobes-simplified-components-lores}
  \caption{
    Velocity components in the outer lobes,
    which have been identified in the \oiii{} slits.
    (a)~Blue-shifted components identified in individual slits.
    (b)~Red-shifted components identified in individual slits.
  }
  \label{fig:outer-lobe-components}
\end{figure*}

\begin{figure}
  \centering
  % \includegraphics[width=\linewidth]{figs/turtle-halo-map-lores}
  \includegraphics[width=\linewidth]{figs/turtle-halo-map}
  \caption{
    Velocity components in the halo, all measured from the \oiii{} spectra with slit positions as indicated.
    Components are divided into three classes:
    inner halo (pink ellipses), outer halo (yellow ellipses),
    and halo knots (green ellipses).
    The inner portion of the background image is
    the same high-pass-filtered \textit{HST} image
    shown in Figs.~\ref{fig:shell-velocity-components} and~\ref{fig:outer-lobe-components}.
    The outer portion of the background image is a deep \oiii{} exposure of the halo
    obtained with MES-SPM in direct imaging mode with an occulting bar (see Fig.~\ref{fig:halo-knots}).
  }
  \label{fig:halo-components}
\end{figure}
